\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%For Listings:
\usepackage{listings}
\lstset{
  frame=single,
  language=C,
  basicstyle=\footnotesize,
}
\makeatletter
\def\lst@makecaption{%
  \def\@captype{table}%
  \@makecaption
}
\makeatother
\begin{document}

\title{Task-based Analysis of OpenMP and HPX}

\author{
\IEEEauthorblockN{Tobias Schiffmann}
\IEEEauthorblockA{
\textit{Universität Stuttgart}\\
Stuttgart, Germany \\
st169736@stud.uni-stuttgart.de}
}

\maketitle

\begin{abstract}
Task-based programming is used to parallelize irregular structures like recursive function calls.
A prominent examples for run time systems allowing to utilize tasks are OpenMP and HPX.
OpenMP is the de facto standard for shared memory parallel programming and in contrast to this HPX is a rather new run time system designed for task-based programming.

These two systems have not yet been compared concerning tasking performance.
To do so the Fibonacci, Merge Sort and a generic algorithm are implemented using both run time systems.

The performances of the executions are compared and some optimization ideas are evaluated.

It comes clear that both run time systems have structures they perform better with compared to the other system.
HPX has problems managing high amounts of small tasks in hierarchical structure, however it achieves better performance with bigger tasks and non hierarchical structures.
\end{abstract}

\begin{IEEEkeywords}
High Performance Computing, HPX, OpenMP, Task-based Parallelism
\end{IEEEkeywords}

\input{sections/Introduction.tex}


\input{sections/RelatedWord.tex}

\input{sections/Implementation.tex}

\input{sections/Environment}

\input{sections/Results}

\input{sections/Optimization}

\input{sections/Conclusion}


\bibliographystyle{unsrt}
\bibliography{paper}{}

\end{document}


% Maybe extensions
% compare with BOTS - fib / sort
% 